\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-25 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

    \item We can then evaluate the accuracy of each estimation method by comparing the size of the confidence intervals of the $\beta$, for each couple $i,s$ (by year and transport mode). We summarize this comparison in Figure \ref{fig:accuracy_beta}, which reports the distribution of the ratio of confidence intervals, taken in log.

    \begin{figure}[htbp]
    \caption{Accuracy of the estimation of the $\beta$: Comparison}
    \label{fig:accuracy_beta}
    \begin{center}
    \includegraphics[height=3in]{../../revised_article/comparaison_amplitude_baseline_referee1_2013_ves.png}
    \begin{minipage} [c]  {5in} \scriptsize%
    	    Note: Ratio of the confidence intervals = $ _{}ln(CI_{is}/CI^{ref}_{is})$
    \end{minipage}

    \end{center}
    \end{figure}

In most cases, the log of the ratio is negative, implying a smaller interval confidence of the baseline $\beta$ estimation. Our method thus yields more accurate estimations of the share of additive components, whatever the transport mode considered. We have checked that a similar conclusion applies on other years (they are not reported here for sake of brevity but they are available upon request).
    \end{itemize}

### 2021-11-25 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee2.tex

\date{November 2021}
 \maketitle
\bigskip

We would like to thank you for your insightful comments. They led us to introduce some
significant changes to the paper that we hope address your concerns. We first give you an overview
of the revision (Section \ref{sec:main_changes}) before answering in detail each of your comments (Section \ref{sec:detailed_answers}). Number of sections, pages and equations mentioned in the text refer to the revised version. When necessary, we refer to number of sections, pages and equations from the submitted version. In this case, they are written into brackets.

\section{Main changes \label{sec:main_changes}}

The structure of the paper has been significantly modified along the revision process, in particular to take into account the referees' comments.
\begin{itemize}
	\item In the submitted version, [Section 2] was devoted to the estimation of international transport costs; specifically, their break-down in two components, additive and ad-valorem. In [Section 3], we investigated the role of additive costs in the decomposition of transport costs time trends, between structural changes and composition effects. [Section 4] was devoted to the robustness analysis relative to the results from both previous sections.
	\item In the revised version, we have substantially strengthened the robustness checks regarding the estimation of international transport costs, with the addition of detailed checks to aggregation and endogeneity. Accordingly, the previously-called [Section 2] has been split in two Sections: Section 2, where we present the data and the estimation strategy; and Section 3, where we present the results. Section 3 now includes the robustness checks as a final sub-section. For the sake of space, the robustness analysis related to composition effects has been sent to the Appendix (Section C.3).
	\item Both referees asked us to devote more developments to the implications of additive costs (the ``Big Picture''). We do agree that this was not emphasized enough in the submitted version, and we thank the referees for their suggestions on that issue. The revised version answers this concern in two points.
	\begin{enumerate}
		\item We maintain the analysis of the transport costs time trends (previously [Section 3], now Section 4); but we improved this section's readability by leaving the technical aspects in the Appendix (Section C). As such, we hope that the main message of this Section is easier to understand.
		\item Most importantly, we now emphasize the ``Big Picture'' welfare implications of additive costs on theoretical grounds. Through the lens of the \cites{melitz} model amended to integrate additive costs, we analyze the welfare gains deriving from the reduction in international transport costs estimated in Section 3 over 1974-2019. In this regard, we shed light on the welfare variations induced by the ``hyper-globalization'' period. This also allows us to quantify the extra welfare gains attributable to reduction of additive trade costs. This analysis is performed in Section 5.

@@

\textbf{Our answer:} We devoted a lot of thought to this point, which directly echoed a similar concern by the other referee. The latter writes: ``\emph{Does this observation revise our understanding of say the gains from trade? Does it shed new light on a puzzle many people are thinking about? [One] suggestion is to dig deeper into the relative rate at which additive and multiplicative transport costs have declined over time.}
''

All in all, your suggestion and the other referee's one pointed toward two possible options for the ``Big Picture'' implications of our exercise: either exploring the compositional country-product dynamics underlying our results, or focusing on the welfare implications. Both paths were undeniably worth exploring, but could not be followed in a single paper. Therefore, we decided to focus on the second path, i.e. to  offer insights on the welfare implications of our results. In this regard, the new Section 5 ``The role of additive cost: Theoretical insights'' is devoted to a theory-based analysis of the changes to welfare gains implied by the relative variations of additive and multiplicative transport costs over our period of analysis.

Our choice to dig into the welfare implications of our results has two main motivations. Firstly, even if ``\emph{the fact that transport costs are both specific and ad-valorem is well known}'', some recent literature still debates the practical importance of additive costs - for example, \cite{Lashkaripour_JIE2020} finds evidence supporting the ad-valorem assumption for denumerable goods, and consistently finds a very small welfare effect of additive costs within a partial-equilibrium model with perfect competition. Secondly, the implications of additive costs have not been fully exhausted in \citet{Irrazabal_2015}, \cite{Hornok-et-al-JIE-2015,Hornok-et-al-RES-2015}, \cite{Alessandria-et-al-AER-2010} or \citet{sorensen2014}. \cite{Kropf-Saure-JIE-2016} estimate the size and shape of per-shipment costs based on Swiss data. \cite{Alessandria-et-al-AER-2010} and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating ``lumpiness'' in international trade transactions. \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. We complement these various outcome by providing a long-run characterization of both additive and multiplicative component of transport costs. Based on these empirical results, we investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019. In this regard, we shed light on the welfare variations induced by the ``hyper-globalization'' period, as well as the key role of additive transport costs in determining those welfare variations.\smallskip

To this aim, we introduce additive costs in the canonical \citet{melitz} model. The inclusion of additive costs in a New Trade model has already been performed in \citet{sorensen2014} and \citet{Irrazabal_2015}. However, \citet{sorensen2014} exclusively provides a theoretical analysis, without any quantitative exercise. In a version of the \citet{chaney2008} model amended for additive costs, \citet{Irrazabal_2015} perform a quantitative simulation to assess the welfare variations induced by the increase in such additive costs (vs ad-valorem costs). For this, they rely on a calibration for trade costs based on their single-year estimation (for the year 2004), from which they depart by assuming an ad-hoc assumption (specifically, a 5\% increase in the ratio of additive cost to the median fas price). In contrast, our own exercise relies on a several decades of US data, allowing us to highlight the welfare alterations induced over time by the relative dynamics of additive and multiplicative costs, based on the values actually observed in the data over the period 1974-2019 in all their dimensions (additive and ad-valorem).\smallskip

In the new Section 5, we use our estimation results over 1974-2019 (Section 3 of the paper) to implement several comparative statics exercises to investigate the different welfare consequences of alterations to multiplicative and additive costs. In addition, we also assess how the latter results are modified by changes in sunk costs of exports $f_{x}$. To that end, we adjust the share of exporting firms in the US based on \citet{BEJK-AER-03} and \citet{Lincoln_McCallum2018}. In our preferred exercise, we quantify the welfare gains deriving from the joined reduction in the fixed export cost $f_x$ and in the variable transport costs as documented in Section 3 (where the two additive/ad-valorem components decrease). We contrast this with the case where the reduction of total transport costs  is solely attributed to a decrease in ad-valorem costs.

Table 6 in Section 5 of the paper reports the results of these various comparative statics exercises for Air and Vessel transport modes. Specifically, we report the welfare effect of a change in variable transport costs, under both scenarios of a constant and fixed export cost. In our preferred scenario, the reduction in variable transport costs in Air transport generates a 40\% higher welfare gain when such a reduction partly
occurs through the additive component, rather than when it happens through a decrease in ad-valorem costs only. In vessel transport, the
extra welfare gains due to the joined reduction of both transport costs components are more modest, with a magnitude of order of 14\%.

Overall, these results add a substantial contribution to the paper: we are able to provide a quantitative assessment of the welfare gains induced by the decrease in both types of costs (additive and multiplicative) over a 45-year period covering the hyper-globalization moment, and to highlight the respective part of each component in the determination of these gains.
%Note also that not only the inclusion of additive costs in the underlying framework generates large welfare differences, but also that the latter are probably a lower bound of the welfare variations induced by changes in additive \emph{trade} costs, larger than the sole transport costs.

@@

\subsection{Empirical strategy}

\textit{The empirical strategy used to unravel the specific and ad-valorem component in international
transport costs is quite elaborate. [...] To be more specific, why not simply estimate equation (1) while plugging
in equation (3) and (4) for $\tau$ and $t$ respectively? Doing this yields the following estimation equation (\ref{eq:ref2_basis}) in
levels (I have added a time subscript t as well as an additive error term $\epsilon$):}

\begin{equation}
p_{ikt}=\tau_{it}\widetilde{p}_{ikt}+ \tau_{kt}\widetilde{p}_{ikt} + t_{it} + t_{kt} + \epsilon_{ikt}   \label{eq:ref2_basis}
\end{equation}

\textit{I do not see why the authors need the complicated non-linear transformations to do what they aim
for. Estimating Equation (\ref{eq:ref2}) should be relatively easy, for one it is linear, but it would also not require the
inclusion of any country-sector fixed effects [...] which can be easily estimated [...] using the authors' notations [as]:}

@@

\begin{equation}
p_{ikt}= \sum_i \sum_t \alpha_{it}^\tau \mathbbm{1}_{it}\widetilde{p}_{ikt} +  \sum_k \sum_t \alpha_{kt}^\tau \mathbbm{1}_{kt}\widetilde{p}_{ikt} + \sum_i \sum_t \alpha_{it}^t \mathbbm{1}_{it} + \sum_k \sum_t \alpha_{it}^t\mathbbm{1}_{kt} \label{eq:ref2}
\end{equation}

\textbf{Our answer:} As highlighted by the referee, our estimated equation imposes to use non-linear estimation methods. We agree that resorting on a linear form as the one suggested by the referee would substantially alleviate the computational burden. However, it would have some important drawbacks.

First, it can be noticed that the equation suggested by the referee does not stand in accordance with the assumption we borrow from \cite{Irrazabal_2015}, that the ad-valorem cost is decomposed in its two country/sector dimensions multiplicatively (i.e. approximating $\tau_{is(k)}$ by the product $\tau_i\times \tau_{s(k)}$).

However, even with another formulation, such as the equations (\ref{eq:ref2_basis}) and (\ref{eq:ref2}) suggested by the referee, we would still be constrained to resort to non-linear estimators. This is due to the restrictions imposed \textit{ex-ante} on parameters, i.e. $\tau \geq 1$ and $t\geq 0$, or $0 \leq \beta \leq 1$. Without these restrictions, standard linear, least squares estimates deliver aberrant values with mediocre quality-of-fit. Taking into account $p_{ikt} < \widetilde{p}_{ikt}$ also implies that the error term should be always positive, which we ensure by specifying the error term such that:

@@

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}}-1 =\left(\tau_{i}\times \tau_{k} -1+\frac{t_{i} + t_{k}}{\widetilde{p}_{ik}} \right)\times \exp(\epsilon_{ik})
\end{equation*}
\noindent where $\epsilon_{ik}$ follows a normal law centered on 0.

Taking into account the various positivity constraints finally leads us to estimate:
\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i}\times \tau_{s(k)} -1+\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}} \right) + \epsilon_{ik} \label{eq:model_IetA}
\end{equation}
\noindent which corresponds to Equation (9) in the paper, and where we ensure the positivity constraint on $\tau_x\geq 1$, $t_x \geq 0$ (with  $x = i, s$) by taking the logs of the parameters. This specification requires a non-linear estimation method. We agree that this point was not clarified enough in the submitted version and we thank the referee for pointing this out. We did our best to make the point clearer in the revised version (see section 2.2, more specifically p. 7-8).

We also devote more time to the robustness of the empirical specification. On top of the robustness to the separability assumption (already in the previously submitted version), we also assess the robustness to potential endogeneity and the level of aggregation (Sections 3.3.2 and 3.3.3). We hope that this new version will convince you that our estimation strategy is both relevant and robust.

### 2021-11-25 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
could / would note 11
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>
Travail collectif
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

%\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage[skip=0.5\baselineskip]{caption}
%\usepackage[latin1]{inputenc}
%\usepackage{hyperref}
%\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
%%GD Quand je mets usepackage[utf8]{inputenc} je n'arrive plus à compiler la biblio
%J'ai essayé de débuger : je n'y suis pas arrivé
\usepackage{rotating}
\usepackage{setspace}
\usepackage{lscape}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{vmargin}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage[tableposition=top]{caption}
\usepackage{amsfonts}
\usepackage{bbold}
\usepackage{natbib}
\usepackage{babel,varioref}
\usepackage{bbm}
\usepackage[flushleft]{threeparttable}
%\usepackage{bbold}
%\usepackage[T1]{fontenc}
% JH : impossible de compiler avec le package bbold, remplacé par amsfonts
% LP : impossible de compiler avec le package bbold, remplacé par bbm
\usepackage{upgreek}
\usepackage{comment}
\includecomment{commentGD}
\usepackage[draft]{todonotes}
%\usepackage[disable]{todonotes}
%%GDPour cacher les notes, \usepackage[disable]{todonotes}

@@

\begin{abstract}
International transport costs do have an additive part. How large is it? Does it matter? This paper provides new answers to these questions. Using information contained in the US imports flows from 1974 to 2019, we develop an empirical model that disentangles the ad-valorem and the additive components of international transport costs. The per-unit component of transport costs represents a sizeable share of total transport costs, between 30\% and 45\% depending on the year and the transport mode considered. We then investigate the important consequences of additive costs, under two different perspectives. First, modelling varying additive costs modifies the decomposition of transport costs time trend between the reduction in ``pure'' transport costs and trade composition effects, the latter playing a minor role. Second, we revisit the welfare gains of the transport cost reduction in presence of additive costs. In this regard, we shed light on the welfare variations induced by the ``hyper-globalization'' period, as well as the key role of additive transport costs in determining those welfare variations. Neglecting the additive component substantially underestimates the welfare gains of the transport cost decrease.
\end{abstract}

@@

Our paper also relates to \cite{Kropf-Saure-JIE-2016}, who estimate the size and shape of per-shipment costs based on Swiss data, and to \cite{Alessandria-et-al-AER-2010} or \cite{Hornok-et-al-RES-2015, Hornok-et-al-JIE-2015}. While \cite{Alessandria-et-al-AER-2010}  and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating some ``lumpiness'' in international trade transactions, \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. Also closely related to our paper is the work by \cite{Irrazabal_2015}, which develops a structural framework for inferring relative additive trade costs from firm-level trade data. Using Norwegian firm-level export data for the year 2004, they find that, for the median shipment, additive costs amount to 6\% of the export price multiplied by the ad-valorem cost. Like \cite{Irrazabal_2015}, we show the important role of the additive component of international trade costs. The literature also explores the welfare implications of additive trade costs. \cite{sorensen2014} analytically shows that important welfare gains can be achieved by reducing additive trade costs. Not much progress has yet been made in quantifying such gains, one potential reason being the lack of an empirical characterization of the additive component of trade costs, the one exceptions being \cite{Irrazabal_2015} and \cite{Hornok-et-al-JIE-2015}. In contrast to them, we can exploit the time dimension of our database to quantify the welfare gains of the trade cost reduction since 1974, based on our empirical yearly estimates over 1974-2019 of overall transport costs, as well as by sub-component (additive and ad-valorem).\smallskip

@@

The remainder of the paper is built as follows. Section \ref{sec:data_method} presents the data and the baseline empirical model we use to estimate the values of international transport costs. Section \ref{sec:basic_results} reports the estimation results on a yearly basis throughout the period 1974-2019 by transport mode, explicitly distinguishing between the additive and the ad-valorem components and providing several important robustness checks of our results. The following sections take stock of those results to draw implications for two important debates in economic analysis. In Section \ref{sec:results_trends}, we offer new insights on the origins of the decrease of transport costs over time, by providing a decomposition of the transport costs trend patterns, between what arises from changes in the trade composition (by sector and partner country), and what arises from changes in transport costs \textit{per se}. Section \ref{sec:theory} implements several theory-based calibration exercises to investigate the different welfare consequences of the observed decrease in ad-valorem and additive costs. Section \ref{sec:conclu} concludes.

@@

As detailed below, the use of a non-linear estimator triggers computational limitations that constrain the level of possible detail, especially when covering a long period of time. Hence, our benchmark results estimate international transport costs at the 3-digit classification level, exploiting heterogeneity between products at the SITC-5 classification level. Depending on the year, this leaves us with around 200 3-digit sectors, from around 200 countries of origin (hence, around 400 fixed effects to estimate). We ensure the robustness of these results by conducting two types of alternative estimates: \textit{i),} within each 3-digit sector, exploiting heterogeneity between HS-10 products. Notice that this can theoretically be done from 1989 onwards for which HS-10 data are available; \textit{ii),} running the estimation at the 4-digit sector level (still with 5-digit products) for some selected years. Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation. However, we obtain no substantial difference between the results obtained for the benchmark 3-5 sector-product classification levels and those considering either the 3-10 and 4-5 ones (See Table \ref{tab:summary_results} below and Section B of the online appendix for the 4-5 results; and Table \ref{tab:baseline10}, Section \ref{sec:robustness} for the 3-10 estimation results).

@@

Since Equation (\ref{eq:equation0}) is non-linear, it cannot be estimated using standard linear estimators. All estimates are thus performed using non-linear least squares.\footnote{The basis of the method is to approximate the model by a linear one and to refine the parameters by successive iterations. The intuitive criterion for convergence is that the sum of squares of residuals does not increase from one iteration to the next.
See \cite{Woolridge-Book-2001} for more details.} Yet, the use of a non-linear estimator triggers computational limitations that constrain the level of possible detail, especially when covering a long period of time.
Confronted with this trade-off, we estimate 3-digit level sectoral fixed effects as our benchmark. This amounts to making the additional assumption, that all 5-digit products $k$ in a 3-digit sector $s$ share the same structure of costs.\footnote{One way to gauge the relevance of this assumption is to provide a decomposition variance exercise on the observed cif-fas price.
As reported in the Online Appendix, Section D.1, the share of the observed variance that is accounted for by the between-sectors ($s$) variance is roughly similar to the between-product ($k$) variance.}$^{,}$\footnote{One may object that we could preserve the estimation at the 5-digit level by running an OLS estimation on the equation taken in level, i.e.
on the basis of Equation (\ref{eq:base_estimee}), specifying the error term additively.
This would not solve the problem though, for three complementary reasons.
First, at the 5-digit level the number of fixed effects to include in the estimation would be more than 430,000 (with 216 countries and 2,029 products), making the estimation computationally extremely burdensome, even in OLS.
Imposing Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}) to reduce the number of fixed effects would drive us back to the non-linearity issue for fixed effects.
Second, making the error term (specified as following a normal law centered on 0) enter Equation (\ref{eq:base_estimee}) additively implies negative values for some of the estimated residuals $\widehat{\epsilon}_{ik}$, which is inconsistent with the constraint that $\frac{p_{ik}}{\widetilde{p}_{ik}}>1$. In a related manner, we could not impose positivity constraints on the coefficients. Third, estimating the equation in level does not eliminate the fact that it is non-linear by nature, as long as there are additive costs to estimate (see Equation (\ref{eq:base_estimee}) for $t_{ik} \neq 0$).}

@@

In both transport modes, the additive component appears of sizable importance throughout the period.
Confirming the results obtained in Table \ref{tab:summary_results}, this suggests that additive costs play a substantial role in total transport costs throughout the period. If the share of additive costs in total costs roughly amounts to 44\% (30\%) in vessel (air) transport on average, one can further notice that it varies substantially over time, with a different pattern across transport modes. After a period of common increase in air and vessel from the mid 1970s to the end of the 1980s, it has steadily decreased for air transport. In contrast, the share of additive costs has continued to increase until the 2000s. Put differently, the total transport costs decrease is disproportionately related to additive costs in air transport, while it is mostly driven by ad-valorem cost reduction in vessel transport.\smallskip

@@

One may be concerned that the specification of Equations (\ref{eq:model_IetA}) or (\ref{eq:model_nlI}) is subject to an endogeneity bias, as the price set by the exporter may vary depending on the transport cost burden. Studies on the pricing-to-market behavior of firms (see \citealp{Krugman-87}) show that we cannot exclude that the export price set by the firm ($\widetilde{p}_{ik}$) is partly endogenous to the size of transport costs (for instance, the exporting firm absorbing (part of) the transport costs by reducing the fas price).
Related concerns may arise from productivity-sorting model in \cite{melitz} or the quality-sorting model in \cite{baldwin_harrigan}: more productive firms and/or firms selling high-quality products will charge different prices, all other things equal – in our case, for a given country-sector pair. In addition, there is also the possibility that bigger firms might impact transport costs, due to their ability of bargaining discounts for larger shipped volumes.

@@

While our benchmark estimates exploit product variability at the 5-digit level, one may wonder about the importance of the disaggregation level in driving the results. In this section, we check the robustness to the use of more disaggregate data within sector.
Current data are available at the 10-digit level for products (HS10) for some specific years. The results reported here rely on exploiting data from 2005 to 2019. This period is obviously smaller than our main sample, due to two main issues. Firstly, we could only access the years 1997-1999 and 2001-2019.\footnote{Theoretically, they should be available from 1989, which is already smaller than our full sample starting in 1974. Because of the COVID situation, it was only possible to get access to the years 1997-1999 and 2001-2019.} Secondly, for the years 1997-1999 and 2001-2005, compatibility issues between Census and Hummels' data (which we use until 2004) prevented reliable comparisons.

>>>>

%\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage[skip=0.5\baselineskip]{caption}
%\usepackage[latin1]{inputenc}
%\usepackage{ref}
%\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
%%GD Quand je mets usepackage[utf8]{inputenc} je n'arrive plus à compiler la biblio
%J'ai essayé de débuger : je n'y suis pas arrivé
\usepackage{rotating}
\usepackage{setspace}
\usepackage{lscape}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{vmargin}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage[tableposition=top]{caption}
\usepackage{amsfonts}
\usepackage{bbold}
\usepackage{natbib}
\usepackage{babel,varioref}
\usepackage{bbm}
\usepackage[flushleft]{threeparttable}
%\usepackage{bbold}
%\usepackage[T1]{fontenc}
% JH : impossible de compiler avec le package bbold, remplacé par amsfonts
% LP : impossible de compiler avec le package bbold, remplacé par bbm
\usepackage{upgreek}
\usepackage{comment}
\includecomment{commentGD}
\usepackage[draft]{todonotes}
%\usepackage[disable]{todonotes}
%%GDPour cacher les notes, \usepackage[disable]{todonotes}

@@

\begin{abstract}
International transport costs do have an additive part. How large is it? Does it matter? This paper provides new answers to these questions. Using information contained in the US imports flows from 1974 to 2019, we develop an empirical model that disentangles the ad-valorem and the additive components of international transport costs. The per-unit component of transport costs represents a sizeable share of total transport costs, between 30\% and 45\% depending on the year and the transport mode considered. We then investigate the important consequences of additive costs, under two different perspectives. First, modelling varying additive costs modifies the decomposition of transport costs time trend between the reduction in ``pure'' transport costs and trade composition effects, the latter playing a minor role. Second, we revisit the welfare gains of the transport cost reduction in presence of additive costs. In this regard, we shed light on the welfare variations induced by the international trade acceleration and the ``hyper-globalization'', as well as the key role of additive transport costs in determining those welfare variations. Neglecting the additive component substantially underestimates the welfare gains of the transport cost decrease.
\end{abstract}

@@

Our paper also relates to \cite{Kropf-Saure-JIE-2016}, who estimate the size and shape of per-shipment costs based on Swiss data, and to \cite{Alessandria-et-al-AER-2010} or \cite{Hornok-et-al-RES-2015, Hornok-et-al-JIE-2015}. While \cite{Alessandria-et-al-AER-2010}  and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating some ``lumpiness'' in international trade transactions, \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. Also closely related to our paper is the work by \cite{Irrazabal_2015}, which develops a structural framework for inferring relative additive trade costs from firm-level trade data. Using Norwegian firm-level export data for the year 2004, they find that, for the median shipment, additive costs amount to 6\% of the export price multiplied by the ad-valorem cost. Like \cite{Irrazabal_2015}, we show the important role of the additive component in international trade costs.
The literature also explores the welfare implications of additive trade costs.
\cite{sorensen2014} analytically shows that important welfare gains can be achieved by reducing additive trade costs.
Providing an actual quantification is difficult, one potential reason being the lack of an empirical characterization of such costs.
Some recent progress has been made, e.g. by \cite{Irrazabal_2015}, \cite{Hornok-et-al-JIE-2015} and \cite{Lashkaripour_JIE2020}.
In contrast to them, we can exploit the time dimension of our database to quantify the welfare gains of the trade cost reduction since 1974, based on our empirical yearly estimates over 1974-2019 of overall transport costs, as well as by sub-component (additive and ad-valorem).\smallskip

@@

The remainder of the paper is built as follows. Section \ref{sec:data_method} presents the data and the baseline empirical model we use to estimate the values of international transport costs. Section \ref{sec:basic_results} reports the estimation results on a yearly basis throughout the period 1974-2019 by transport mode, explicitly distinguishing between the additive and the ad-valorem components and providing several important robustness checks of our results. The following sections take stock of those results to draw implications for two important debates in economic analysis. In Section \ref{sec:results_trends}, we offer new insights on the decrease of transport costs over time, by providing a decomposition of the transport costs trend patterns, between what arises from changes in the trade composition (by sector and partner country), and what arises from changes in transport costs \textit{per se}. Section \ref{sec:theory} implements several theory-based calibration exercises to investigate the different welfare consequences of the observed decrease in ad-valorem and additive costs. Section \ref{sec:conclu} concludes.

@@

As detailed below, the use of a non-linear estimator triggers computational limitations that constrain the level of possible detail, especially when covering a long period of time. Hence, our benchmark estimation retains the 3-digit sectoral classification level, exploiting heterogeneity between products at the SITC-5 classification level.
Depending on the year, this leaves us with around 200 3-digit sectors, from around 200 countries of origin (hence, around 400 fixed effects to estimate).
We ensure the robustness of these results by conducting two types of alternative estimates: \textit{i),} within each 3-digit sector, exploiting heterogeneity between HS-10 products.
Notice that this can theoretically be done from 1989 onwards for which HS-10 data are available; \textit{ii),} running the estimation at the 4-digit sector level (still with 5-digit products) for some selected years.
Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation.
However, we obtain no substantial difference between the results obtained for the benchmark 3-5 sector-product classification levels and those considering either the 3-10 and 4-5 ones (See Table \ref{tab:summary_results} below and Section B of the online appendix for the 4-5 results; and Table \ref{tab:baseline10}, Section \ref{sec:robustness} for the 3-10 estimation results).

@@

Since Equation (\ref{eq:equation0}) is non-linear, it cannot be estimated using standard linear estimators. All estimates are thus performed using non-linear least squares.\footnote{The basis of the method is to approximate the model by a linear one and to refine the parameters by successive iterations. The intuitive criterion for convergence is that the sum of squares of residuals does not increase from one iteration to the next.
See \cite{Woolridge-Book-2001} for more details.} Yet, the use of a non-linear estimator triggers computational limitations that constrain the level of possible detail, especially when covering a long period of time.
Confronted with this trade-off, we estimate 3-digit level sectoral fixed effects as our benchmark. This amounts to making the additional assumption, that all 5-digit products $k$ in a 3-digit sector $s$ share the same structure of costs.\footnote{One way to gauge the relevance of this assumption is to provide a decomposition variance exercise on the observed cif-fas price.
As reported in the Online Appendix, Section D.1, the share of the observed variance that is accounted for by the between-sectors ($s$) variance is roughly similar to the between-product ($k$) variance.}$^{,}$\footnote{One may object that we could run an OLS estimation on the basis of Equation (\ref{eq:base_estimee}), specifying the error term additively.
This would not solve the problem though, for three complementary reasons.
First, at the 5-digit level the number of fixed effects to include in the estimation would be more than 430,000 (with 216 countries and 2,029 products), making the estimation computationally extremely burdensome, even in OLS.
Imposing Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}) to reduce the number of fixed effects would drive us back to the non-linearity issue for fixed effects.
Second, making the error term (specified as following a normal law centered on 0) enter Equation (\ref{eq:base_estimee}) additively implies negative values for some of the estimated residuals $\widehat{\epsilon}_{ik}$, which is inconsistent with the constraint that $\frac{p_{ik}}{\widetilde{p}_{ik}}>1$.
Third, in a related manner, we would not be able to impose the necessary constraints on the coefficients ($\tau\geq 1, t\geq 0 )$.}
%Third, estimating the equation in level does not eliminate the fact that it is non-linear by nature, as long as there are additive costs to estimate (see Equation (\ref{eq:base_estimee}) for $t_{ik} \neq 0$).

@@

In both transport modes, the additive component appears of sizable importance throughout the period.
Confirming the results obtained in Table \ref{tab:summary_results}, this suggests that additive costs play a substantial role in total transport costs throughout the period. If the share of additive costs in total costs roughly amounts to 44\% (30\%) in vessel (air) transport on average, one can further notice that it varies substantially over time, with a different pattern across transport modes. After a period of common increase in air and vessel from the mid 1970s to the end of the 1980s, it has steadily decreased for air transport. In contrast, the share of additive costs has continued to increase until the 2000s for vessel.
Put differently, the total transport costs decrease mostly comes from the reduction of additive costs in air transport, while it is mainly driven by ad-valorem cost reduction in vessel transport.\smallskip

@@

One may be concerned that the specification of Equations (\ref{eq:model_IetA}) or (\ref{eq:model_nlI}) is subject to an endogeneity bias, as the price set by the exporter may vary depending on the transport cost burden. Studies on the pricing-to-market behavior of firms (see \citealp{Krugman-87}) show that we cannot exclude that the export price set by the firm ($\widetilde{p}_{ik}$) is partly endogenous to the size of transport costs (for instance, the exporting firm absorbing (part of) the transport costs by reducing the fas price).
Related concerns may arise from productivity-sorting model in \cite{melitz} or the quality-sorting model in \cite{baldwin_harrigan}: more productive firms and/or firms selling high-quality products will charge different prices, all other things equal – in our case, for a given country-sector pair. In addition, there is also the possibility that bigger firms might impact transport costs, due to their ability for bargaining discounts for larger shipped volumes.

@@

While our benchmark estimates exploit product variability at the 5-digit level, one may wonder about the importance of the disaggregation level in driving the results. In this section, we check the robustness to the use of more disaggregate data within sector.
Current data are available at the 10-digit level for products (HS10) for some specific years. The results reported here rely on exploiting data from 2005 to 2019. This period is obviously smaller than our main sample, due to two main issues. Firstly, we could only access the years 1997-1999 and 2001-2019.\footnote{Theoretically, they should be available from 1989, which is already smaller than our full sample starting in 1974. Because of the COVID situation, it was only possible to get access to the years 1997-1999 and 2001-2019.} Secondly, for the years 1997-1999 and 2001-2004, compatibility issues between Census and Hummels' data (which we use until 2004) prevented reliable comparisons.
